### 2023-12-24 sections/4-results.tex
moved Morgan's changes
shortened table captions, bolded dataset names

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the fashion-mnist dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 1.33~$\times10^{4}$ & 0.954 & 2.19~$\times10^{3}$ & 0.950 & 2.13~$\times10^{2}$  & 1.000 & 2.01~$\times10^{3}$ & 1.000* & 2.17~$\times10^{3}$ & 1.000 \\
                    \hline
                    2   & 1.38~$\times10^{4}$ & 0.803 & 2.12~$\times10^{3}$ & 0.927 & 1.06~$\times10^{2}$  & 1.000 & 9.39~$\times10^{2}$ & 1.000* & 1.14~$\times10^{3}$ & 1.000 \\
                    \hline
                    4   & 1.66~$\times10^{4}$ & 0.681 & 2.04~$\times10^{3}$ & 0.898 & 5.31~$\times10^{1}$  & 1.000 & 4.61~$\times10^{2}$ & 0.997  & 9.82~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 1.68~$\times10^{4}$ & 0.525 & 1.93~$\times10^{3}$ & 0.857 & 2.66~$\times10^{1}$  & 1.000 & 2.26~$\times10^{2}$ & 0.995  & 1.18~$\times10^{3}$ & 1.000 \\
                    \hline
                    16  & 1.87~$\times10^{4}$ & 0.494 & 1.84~$\times10^{3}$ & 0.862 & 1.33~$\times10^{1}$  & 1.000 & 1.17~$\times10^{2}$ & 0.991  & 1.20~$\times10^{3}$ & 1.000 \\
                    \hline
                    32  & 1.56~$\times10^{4}$ & 0.542 & 1.85~$\times10^{3}$ & 0.775 & 6.65~$\times10^{0}$  & 1.000 & 5.91~$\times10^{1}$ & 0.985  & 1.16~$\times10^{3}$ & 1.000 \\
                    \hline
                    64  & 1.50~$\times10^{4}$ & 0.378 & 1.78~$\times10^{3}$ & 0.677 & 3.32~$\times10^{0}$  & 1.000 & 2.61~$\times10^{1}$ & 0.968  & 1.10~$\times10^{3}$ & 1.000 \\
                    \hline
                    128 & 1.49~$\times10^{4}$ & 0.357 & 1.66~$\times10^{3}$ & 0.538 & 1.66~$\times10^{0}$  & 1.000 & 1.33~$\times10^{1}$ & 0.964  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                    256 & --                  & --    & 1.60~$\times10^{3}$ & 0.592 & 8.31~$\times10^{-1}$ & 1.000 & 6.65~$\times10^{0}$ & 0.962  & 1.06~$\times10^{3}$ & 1.000 \\
                    \hline
                    512 & --                  & --    & 1.83~$\times10^{3}$ & 0.581 & 4.16~$\times10^{-1}$ & 1.000 & 3.56~$\times10^{0}$ & 0.949  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the glove-25 dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-glove-25}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 2.28~$\times10^{4}$ & 0.801 & 2.83~$\times10^{3}$ & 0.835 & 2.78~$\times10^{2}$ & 1.000 & 2.38~$\times10^{3}$ & 1.000* & 7.22~$\times10^{2}$ & 1.000 \\
                    \hline
                    2   & 2.38~$\times10^{4}$ & 0.607 & 2.70~$\times10^{3}$ & 0.832 & 1.39~$\times10^{2}$ & 1.000 & 1.19~$\times10^{3}$ & 1.000* & 5.75~$\times10^{2}$ & 1.000 \\
                    \hline
                    4   & 2.50~$\times10^{4}$ & 0.443 & 2.61~$\times10^{3}$ & 0.839 & 6.98~$\times10^{1}$ & 1.000 & 6.19~$\times10^{2}$ & 1.000* & 6.25~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 2.78~$\times10^{4}$ & 0.294 & 2.51~$\times10^{3}$ & 0.834 & 3.49~$\times10^{1}$ & 1.000 & 3.03~$\times10^{2}$ & 1.000* & 5.93~$\times10^{2}$ & 1.000 \\
                    \hline
                    16  & 3.11~$\times10^{4}$ & 0.213 & 2.23~$\times10^{3}$ & 0.885 & 1.74~$\times10^{1}$ & 1.000 & 1.51~$\times10^{2}$ & 1.000* & 5.49~$\times10^{2}$ & 1.000 \\
                    \hline
                    32  & 3.24~$\times10^{4}$ & 0.178 & 2.01~$\times10^{3}$ & 0.764 & 8.70~$\times10^{0}$ & 1.000 & 7.40~$\times10^{1}$ & 0.999  & 4.75~$\times10^{2}$ & 1.000 \\
                    \hline
                    64  & --                  & --    & 1.99~$\times10^{3}$ & 0.631 & 4.36~$\times10^{0}$ & 1.000 & 3.77~$\times10^{1}$ & 0.997  & 4.61~$\times10^{2}$ & 1.000 \\
                    \hline
                    128 & --                  & --    & --                  & --    & 2.18~$\times10^{0}$ & 1.000 & 1.90~$\times10^{1}$ & 0.998  & 4.41~$\times10^{2}$ & 1.000 \\
                    \hline
                    256 & --                  & --    & --                  & --    & 1.07~$\times10^{0}$ & 1.000 & 9.47~$\times10^{0}$ & 0.998  & 4.23~$\times10^{2}$ & 1.000 \\
                    \hline
                    % 512 & -- & -- & -- & -- & 0.544 & 1.000 & 4.499 & 0.996 & 0.000 & 0.000 \\
                    % \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the sift dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-sift}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1   & 1.93~$\times10^{4}$ & 0.782 & 3.98~$\times10^{3}$ & 0.686 & 7.26~$\times10^{1}$  & 1.000 & 6.98~$\times10^{2}$ & 1.000* & 5.52~$\times10^{2}$ & 1.000 \\
                    \hline
                    2   & 2.03~$\times10^{4}$ & 0.552 & 3.80~$\times10^{3}$ & 0.614 & 3.62~$\times10^{1}$  & 1.000 & 3.30~$\times10^{2}$ & 1.000* & 2.66~$\times10^{2}$ & 1.000 \\
                    \hline
                    4   & 2.18~$\times10^{4}$ & 0.394 & 3.69~$\times10^{3}$ & 0.637 & 1.82~$\times10^{1}$  & 1.000 & 1.65~$\times10^{2}$ & 1.000* & 1.43~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 2.48~$\times10^{4}$ & 0.298 & 3.58~$\times10^{3}$ & 0.710 & 9.08~$\times10^{0}$  & 1.000 & 7.72~$\times10^{1}$ & 1.000* & 7.94~$\times10^{1}$ & 1.000 \\
                    \hline
                    16  & 2.68~$\times10^{4}$ & 0.210 & 3.50~$\times10^{3}$ & 0.690 & 4.54~$\times10^{0}$  & 1.000 & 3.98~$\times10^{1}$ & 1.000* & 8.12~$\times10^{1}$ & 1.000 \\
                    \hline
                    32  & 2.75~$\times10^{4}$ & 0.193 & 3.44~$\times10^{3}$ & 0.639 & 2.27~$\times10^{0}$  & 1.000 & 2.09~$\times10^{1}$ & 0.999  & 7.81~$\times10^{1}$ & 1.000 \\
                    \hline
                    64  & --                  & --    & 3.39~$\times10^{3}$ & 0.678 & 1.14~$\times10^{0}$  & 1.000 & 8.87~$\times10^{0}$ & 0.997  & 7.43~$\times10^{1}$ & 1.000 \\
                    \hline
                    128 & --                  & --    & 3.36~$\times10^{3}$ & 0.643 & 5.66~$\times10^{-1}$ & 1.000 & 4.78~$\times10^{0}$ & 0.993  & 6.80~$\times10^{1}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on a random dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-random}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1  & 1.17~$\times10^{4}$ & 0.060 & 4.28~$\times10^{3}$ & 0.028 & 7.16~$\times10^{1}$ & 1.000 & 7.34~$\times10^{2}$ & 1.000* & 5.54~$\times10^{2}$ & 1.000 \\
                    \hline
                    2  & 1.01~$\times10^{4}$ & 0.048 & 4.04~$\times10^{3}$ & 0.021 & 3.62~$\times10^{1}$ & 1.000 & 3.58~$\times10^{2}$ & 1.000* & 2.69~$\times10^{2}$ & 1.000 \\
                    \hline
                    4  & 9.12~$\times10^{3}$ & 0.031 & 3.64~$\times10^{3}$ & 0.014 & 1.81~$\times10^{1}$ & 1.000 & 1.90~$\times10^{2}$ & 1.000* & 1.37~$\times10^{2}$ & 1.000 \\
                    \hline
                    8  & 8.35~$\times10^{3}$ & 0.022 & 3.37~$\times10^{3}$ & 0.013 & 9.04~$\times10^{0}$ & 1.000 & 8.84~$\times10^{1}$ & 1.000* & 5.69~$\times10^{1}$ & 1.000 \\
                    \hline
                    16 & 8.25~$\times10^{3}$ & 0.008 & 3.17~$\times10^{3}$ & 0.006 & 4.53~$\times10^{0}$ & 1.000 & 4.36~$\times10^{1}$ & 1.000* & 2.61~$\times10^{1}$ & 1.000 \\
                    \hline
                    32 & --                  & --    & 3.01~$\times10^{3}$ & 0.007 & 2.27~$\times10^{0}$ & 1.000 & 1.72~$\times10^{1}$ & 1.000* & 1.35~$\times10^{1}$ & 1.000 \\
                    % \hline
                    % 64 & -- & -- & -- & -- & 1.135 & 1.000 & 9.939 & 1.000 & 0.000 & 0.000 \\
                    % \hline
                    % 128 & --& -- & -- & -- & 0.567 & 1.000 & 5.106 & 1.000 & 0.000 & 0.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

@@

>>>>

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{fashion-mnist} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 1.33~$\times10^{4}$ & 0.954 & 2.19~$\times10^{3}$ & 0.950 & 2.13~$\times10^{2}$  & 1.000 & 2.01~$\times10^{3}$ & 1.000* & 2.17~$\times10^{3}$ & 1.000 \\
                    \hline
                    2   & 1.38~$\times10^{4}$ & 0.803 & 2.12~$\times10^{3}$ & 0.927 & 1.06~$\times10^{2}$  & 1.000 & 9.39~$\times10^{2}$ & 1.000* & 1.14~$\times10^{3}$ & 1.000 \\
                    \hline
                    4   & 1.66~$\times10^{4}$ & 0.681 & 2.04~$\times10^{3}$ & 0.898 & 5.31~$\times10^{1}$  & 1.000 & 4.61~$\times10^{2}$ & 0.997  & 9.82~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 1.68~$\times10^{4}$ & 0.525 & 1.93~$\times10^{3}$ & 0.857 & 2.66~$\times10^{1}$  & 1.000 & 2.26~$\times10^{2}$ & 0.995  & 1.18~$\times10^{3}$ & 1.000 \\
                    \hline
                    16  & 1.87~$\times10^{4}$ & 0.494 & 1.84~$\times10^{3}$ & 0.862 & 1.33~$\times10^{1}$  & 1.000 & 1.17~$\times10^{2}$ & 0.991  & 1.20~$\times10^{3}$ & 1.000 \\
                    \hline
                    32  & 1.56~$\times10^{4}$ & 0.542 & 1.85~$\times10^{3}$ & 0.775 & 6.65~$\times10^{0}$  & 1.000 & 5.91~$\times10^{1}$ & 0.985  & 1.16~$\times10^{3}$ & 1.000 \\
                    \hline
                    64  & 1.50~$\times10^{4}$ & 0.378 & 1.78~$\times10^{3}$ & 0.677 & 3.32~$\times10^{0}$  & 1.000 & 2.61~$\times10^{1}$ & 0.968  & 1.10~$\times10^{3}$ & 1.000 \\
                    \hline
                    128 & 1.49~$\times10^{4}$ & 0.357 & 1.66~$\times10^{3}$ & 0.538 & 1.66~$\times10^{0}$  & 1.000 & 1.33~$\times10^{1}$ & 0.964  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                    256 & --                  & --    & 1.60~$\times10^{3}$ & 0.592 & 8.31~$\times10^{-1}$ & 1.000 & 6.65~$\times10^{0}$ & 0.962  & 1.06~$\times10^{3}$ & 1.000 \\
                    \hline
                    512 & --                  & --    & 1.83~$\times10^{3}$ & 0.581 & 4.16~$\times10^{-1}$ & 1.000 & 3.56~$\times10^{0}$ & 0.949  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{glove-25} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-glove-25}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 2.28~$\times10^{4}$ & 0.801 & 2.83~$\times10^{3}$ & 0.835 & 2.78~$\times10^{2}$ & 1.000 & 2.38~$\times10^{3}$ & 1.000* & 7.22~$\times10^{2}$ & 1.000 \\
                    \hline
                    2   & 2.38~$\times10^{4}$ & 0.607 & 2.70~$\times10^{3}$ & 0.832 & 1.39~$\times10^{2}$ & 1.000 & 1.19~$\times10^{3}$ & 1.000* & 5.75~$\times10^{2}$ & 1.000 \\
                    \hline
                    4   & 2.50~$\times10^{4}$ & 0.443 & 2.61~$\times10^{3}$ & 0.839 & 6.98~$\times10^{1}$ & 1.000 & 6.19~$\times10^{2}$ & 1.000* & 6.25~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 2.78~$\times10^{4}$ & 0.294 & 2.51~$\times10^{3}$ & 0.834 & 3.49~$\times10^{1}$ & 1.000 & 3.03~$\times10^{2}$ & 1.000* & 5.93~$\times10^{2}$ & 1.000 \\
                    \hline
                    16  & 3.11~$\times10^{4}$ & 0.213 & 2.23~$\times10^{3}$ & 0.885 & 1.74~$\times10^{1}$ & 1.000 & 1.51~$\times10^{2}$ & 1.000* & 5.49~$\times10^{2}$ & 1.000 \\
                    \hline
                    32  & 3.24~$\times10^{4}$ & 0.178 & 2.01~$\times10^{3}$ & 0.764 & 8.70~$\times10^{0}$ & 1.000 & 7.40~$\times10^{1}$ & 0.999  & 4.75~$\times10^{2}$ & 1.000 \\
                    \hline
                    64  & --                  & --    & 1.99~$\times10^{3}$ & 0.631 & 4.36~$\times10^{0}$ & 1.000 & 3.77~$\times10^{1}$ & 0.997  & 4.61~$\times10^{2}$ & 1.000 \\
                    \hline
                    128 & --                  & --    & --                  & --    & 2.18~$\times10^{0}$ & 1.000 & 1.90~$\times10^{1}$ & 0.998  & 4.41~$\times10^{2}$ & 1.000 \\
                    \hline
                    256 & --                  & --    & --                  & --    & 1.07~$\times10^{0}$ & 1.000 & 9.47~$\times10^{0}$ & 0.998  & 4.23~$\times10^{2}$ & 1.000 \\
                    \hline
                    % 512 & -- & -- & -- & -- & 0.544 & 1.000 & 4.499 & 0.996 & 0.000 & 0.000 \\
                    % \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{sift} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-sift}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1   & 1.93~$\times10^{4}$ & 0.782 & 3.98~$\times10^{3}$ & 0.686 & 7.26~$\times10^{1}$  & 1.000 & 6.98~$\times10^{2}$ & 1.000* & 5.52~$\times10^{2}$ & 1.000 \\
                    \hline
                    2   & 2.03~$\times10^{4}$ & 0.552 & 3.80~$\times10^{3}$ & 0.614 & 3.62~$\times10^{1}$  & 1.000 & 3.30~$\times10^{2}$ & 1.000* & 2.66~$\times10^{2}$ & 1.000 \\
                    \hline
                    4   & 2.18~$\times10^{4}$ & 0.394 & 3.69~$\times10^{3}$ & 0.637 & 1.82~$\times10^{1}$  & 1.000 & 1.65~$\times10^{2}$ & 1.000* & 1.43~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 2.48~$\times10^{4}$ & 0.298 & 3.58~$\times10^{3}$ & 0.710 & 9.08~$\times10^{0}$  & 1.000 & 7.72~$\times10^{1}$ & 1.000* & 7.94~$\times10^{1}$ & 1.000 \\
                    \hline
                    16  & 2.68~$\times10^{4}$ & 0.210 & 3.50~$\times10^{3}$ & 0.690 & 4.54~$\times10^{0}$  & 1.000 & 3.98~$\times10^{1}$ & 1.000* & 8.12~$\times10^{1}$ & 1.000 \\
                    \hline
                    32  & 2.75~$\times10^{4}$ & 0.193 & 3.44~$\times10^{3}$ & 0.639 & 2.27~$\times10^{0}$  & 1.000 & 2.09~$\times10^{1}$ & 0.999  & 7.81~$\times10^{1}$ & 1.000 \\
                    \hline
                    64  & --                  & --    & 3.39~$\times10^{3}$ & 0.678 & 1.14~$\times10^{0}$  & 1.000 & 8.87~$\times10^{0}$ & 0.997  & 7.43~$\times10^{1}$ & 1.000 \\
                    \hline
                    128 & --                  & --    & 3.36~$\times10^{3}$ & 0.643 & 5.66~$\times10^{-1}$ & 1.000 & 4.78~$\times10^{0}$ & 0.993  & 6.80~$\times10^{1}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on a \textbf{random} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-random}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1  & 1.17~$\times10^{4}$ & 0.060 & 4.28~$\times10^{3}$ & 0.028 & 7.16~$\times10^{1}$ & 1.000 & 7.34~$\times10^{2}$ & 1.000* & 5.54~$\times10^{2}$ & 1.000 \\
                    \hline
                    2  & 1.01~$\times10^{4}$ & 0.048 & 4.04~$\times10^{3}$ & 0.021 & 3.62~$\times10^{1}$ & 1.000 & 3.58~$\times10^{2}$ & 1.000* & 2.69~$\times10^{2}$ & 1.000 \\
                    \hline
                    4  & 9.12~$\times10^{3}$ & 0.031 & 3.64~$\times10^{3}$ & 0.014 & 1.81~$\times10^{1}$ & 1.000 & 1.90~$\times10^{2}$ & 1.000* & 1.37~$\times10^{2}$ & 1.000 \\
                    \hline
                    8  & 8.35~$\times10^{3}$ & 0.022 & 3.37~$\times10^{3}$ & 0.013 & 9.04~$\times10^{0}$ & 1.000 & 8.84~$\times10^{1}$ & 1.000* & 5.69~$\times10^{1}$ & 1.000 \\
                    \hline
                    16 & 8.25~$\times10^{3}$ & 0.008 & 3.17~$\times10^{3}$ & 0.006 & 4.53~$\times10^{0}$ & 1.000 & 4.36~$\times10^{1}$ & 1.000* & 2.61~$\times10^{1}$ & 1.000 \\
                    \hline
                    32 & --                  & --    & 3.01~$\times10^{3}$ & 0.007 & 2.27~$\times10^{0}$ & 1.000 & 1.72~$\times10^{1}$ & 1.000* & 1.35~$\times10^{1}$ & 1.000 \\
                    % \hline
                    % 64 & -- & -- & -- & -- & 1.135 & 1.000 & 9.939 & 1.000 & 0.000 & 0.000 \\
                    % \hline
                    % 128 & --& -- & -- & -- & 0.567 & 1.000 & 5.106 & 1.000 & 0.000 & 0.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

@@

Tables~\ref{table:results:fashion}, ~\ref{table:results:glove-25}, ~\ref{table:results:sift}, and ~\ref{table:results:random} show the throughput and recall of CAKES's algorithms at each cardinality multiplier (i.e., scale) for the fashion-mnist, glove-25, sift, and random datasets respectively. When reporting recall, we use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.

% We need to redo this plot so that we do not actually augment random datasets but instead take larger and larger 
% random datasets
% 
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=3.4in]{plots/random-1000000-128-knn-10.png}
%     \caption{
%         Algorithm performance by cardinality multiplier on a random dataset for $k=10$.
%     }
%     \label{fig:results:random-scaling}
% \end{figure}
